
As pointed out by the book, we should take care of the
machine float numbers since it introduces error.

\subsection{Roots of equations}

Find a solution $x^*$ so that $f(x^*)=0$.

1. Dichotomy.

2. Iterative method and Aitken method.

3. Newton method and secant method.

\subsection{Linear equations}

Solving $Ax=b$.

LU-decomposition.

1. Gauss elimination.

2. Iterative method. Gradient descent, Jacobi iterative method, Gauss-Deidel iterative method.

\subsection{Interpolation}

1. Lagrange interpolation polynomial.

2. Newton interpolation polynomial.

3. Piecewise interpolation polynomial.

4. Spline interpolation.

\subsection{Curve Fitting}

Least square method. $min \frac{1}{2}|| \hat{x} - x ||^2$.

For overdetermined equations $A\vec{x}=\vec{b}$, we are looking for a set of
value $\vec{x^*}$ so that $|| A\vec{x^*} - b ||^2$ can be minimized.

$$\varphi(\vec{x}) = \sum_{i=1}^m \delta_i^2 = \sum_{i=1}^m 
  (\sum_{j=1}^n a_{ij}x_j - b_i )^2 $$
$$ \frac{\partial \varphi}{\partial x_k} = 
  2\sum_{i=1}^m \sum_{j=1}^n (a_{ij}x_j-b_i)a_{ik} = 0 (k=1,2,...,n) $$
i.e. $A^T A x = A^T b $.

\subsection{Numerical integration and differentiation}

1. Simpson formula, Cotes formula.

2. Romberg formula.

3. Gauss integration formula.

\subsection{Ordinal differential equation, ODE}

1. Euler formula.

2. Runge-Kutta formula.

3. Adams.

There is a useful trick which converts a high order equation into a group
of the first order equations. E.g. given that $ y'' = f(x,y,y') $,
$y(a)=\alpha$, $y(b)=\beta$, then we introduce $z=y'$,
and we get $y'=z$, $y(a)=\alpha$, $z'=f(x,y,z)$, $z(a)=\beta$.

\subsection{Eigen Value and Eigen Vector}

Find a pair of non-zero eigen value $\lambda$ and non-zero eigen vector $x$ from
$(\lambda I - A)x = 0$.

1. Jacobi.

2. QR method.
